An Event-based Architecture for Multi-population Optimization Algorithms

### 2020-01-27 draft.tex
Some aclarations and references to literature

We show another pool-based approach in Figure  \ref{fig:population_pool}. In
this design, the global population is stored in a central repository, while
isolated algorithms take random samples of the global population and use this
temporal subpopulation as parameters. An advantage of this design is that the
sampling provides a type of migration between isolated subpopulations. A problem
found is that when a processing node returns a subpopulation to the pool, the
state of the subpopulation is lost. But having the algorithm decoupled opens the
possibility of a serverless-function implementation.

@@

In this work, we implemented all message
queues in the Redis memory store. Each queue is a Redis List object, and we use
the \texttt{LPOP} (left pop), and \texttt{RPOP} (right pop) commands for a queue like behavior.
In those cases where we needed a blocking behavior, i.e., when a process needs
to wait until a message is available, we used the blocking versions \texttt{BLPOP} and
\texttt{BRPOP}. Redis in-memory operation are very fast, and all of the obove 
operations have a time complexity of $\mathcal{O}(1)$. We use the official 
\texttt{redis:alpine} container image from DockerHub.

>>>>

We show another pool-based approach in Figure  \ref{fig:population_pool}. In
this design, the global population is stored in a central repository, while
isolated algorithms take random samples of the global population and use this
temporal subpopulation as parameters. An advantage of this design is that the
sampling provides a type of migration between isolated subpopulations. A problem
found is that when a processing node returns a subpopulation to the pool, the
state of the subpopulation is lost. But having the algorithm decoupled opens the
possibility of implementing the system using serverless functions.

@@

In this work, we implemented all message
queues in the Redis memory store. Early cloud architectures
\cite{de2017parallel} used queues for communication, although in that
case RabbitMQ was the chosen tool. Redis is faster, and also can act
as a data store from where we can control the state of the application.
Each queue is a Redis List object, and we use
the \texttt{LPOP} (left pop), and \texttt{RPOP} (right pop) commands for a queue like behavior.
In those cases where we needed a blocking behavior, i.e., when a process needs
to wait until a message is available, we used the blocking versions \texttt{BLPOP} and
\texttt{BRPOP}. Redis in-memory operation are very fast, and all of the obove 
operations have a time complexity of $\mathcal{O}(1)$. We use the official 
\texttt{redis:alpine} container image from DockerHub.
